Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration

### 2022-05-08 manuscript_covid19dashboard.Rmd
Updated literature review

Dashboards are one of the best visual interpretation method of tracking the spread & communication of COVID-19 pandemic. Initially 15 dashboards were compared  to determine which data types are most frequently shown in dashboards. The 15 dashboards we used in the study are listed below (Table 1). We compared dashboards to identify the different features, visualization
methods and improvements that should be occurred.

@@

First, dashboards were compared to determine which data types are most frequently shown in dashboards. The results are shown in Table 02.

@@

As shown in table 02 all dashboards which are considered in this paper represent the data related to COVID-19 confirmed cases, recovered cases & deaths. There have been contained vaccination details, 8 dashboards out of 15 dashboards. In almost each & every dashboard, value boxes have been used to represent these total figures. Bar charts & line charts (trend lines) are most frequently used to visualize these data (confirmed cases, recovered cases, deaths & vaccination details) with respect to time. A Majority of dashboards presented data by daily or weekly. The mapping is used to track the spatial distribution of COVID-19 cases by country/ provincial/ regional etc. When visualizing the data by map color code system & circles with respect to the size of the cases have been used to visualize the variation in size. The considerable number of dashboards has been used doughnut shape pie charts to represent total COVID-19 confirmed cases, recovered cases, active cases & deaths as a percentage. Also, region, gender, age group & ethnicity can be identified as common breakdowns of COVID-19 cases. In some dashboard has been added data tables for representing cases distribution by province/region.  Only very few dashboards have been visualized in COVID-19 test details. Only 6 dashboards have been compared to global situations. In addition, fatality rate, incidence rate, ICU beds, stage of the patients & hospitalize details have been contained in the several dashboards. These are the most common data types that have been contained in the dashboards. The main tools that have been used for different purpose can be shown in the following table.\hfill\break

>>>>

Dashboards are one of the best visual interpretation methods for tracking the spread and communication of the COVID-19 pandemic. The 15 dashboards we used in the literature survey are listed in Table 1. We compared dashboards to identify data types, plotting techniques, colour themes, and other features such as interactivity on plots and panel numbers.

@@

Table 02 summarizes the data types that are most frequently shown in dashboards. As shown in Table 02, all dashboards which are considered in this paper represent the data related to COVID-19 confirmed cases, recovered cases, and deaths. There were 8 dashboards out of 15 dashboards that contained vaccination details.

@@

Table 03 summarizes the visualization methods used in the dashboards. In almost every dashboard, value boxes have been used to represent these total figures. Bar charts and line charts (trend lines) are most frequently used to visualize this data (confirmed cases, recovered cases, deaths, and vaccination details) with respect to time. A majority of dashboards presented data either daily or weekly. The mapping is used to track the spatial distribution of COVID-19 cases by country, province, regional etc. When visualizing the data by the map color code system, circles with respect to the size of the cases have been used to visualize the variation in size. The considerable number of dashboards has been used in doughnut-shaped pie charts to represent total COVID-19 confirmed cases, recovered cases, active cases, and deaths as a percentage. Also, region, gender, age group, and ethnicity can be identified as common breakdowns of COVID-19 cases. Data tables for representing case distribution by province/region have been added to some dashboards. Very few dashboards have been visualized in the COVID-19 test details. Only 6 dashboards have been compared to global situations. In addition, the fatality rate, incidence rate, ICU beds, stage of the patients, and hospitalized details have been contained in the several dashboards.\hfill\break

### 2022-05-08 manuscript_covid19dashboard.tex
Updated literature review

Dashboards are one of the best visual interpretation method of tracking
the spread \& communication of COVID-19 pandemic. Initially 15
dashboards were compared to determine which data types are most
frequently shown in dashboards. The 15 dashboards we used in the study
are listed below (Table 1). We compared dashboards to identify the
different features, visualization methods and improvements that should
be occurred.

@@

As shown in table 02 all dashboards which are considered in this paper
represent the data related to COVID-19 confirmed cases, recovered cases
\& deaths. There have been contained vaccination details, 8 dashboards
out of 15 dashboards. In almost each \& every dashboard, value boxes
have been used to represent these total figures. Bar charts \& line
charts (trend lines) are most frequently used to visualize these data
(confirmed cases, recovered cases, deaths \& vaccination details) with
respect to time. A Majority of dashboards presented data by daily or
weekly. The mapping is used to track the spatial distribution of
COVID-19 cases by country/ provincial/ regional etc. When visualizing
the data by map color code system \& circles with respect to the size of
the cases have been used to visualize the variation in size. The
considerable number of dashboards has been used doughnut shape pie
charts to represent total COVID-19 confirmed cases, recovered cases,
active cases \& deaths as a percentage. Also, region, gender, age group
\& ethnicity can be identified as common breakdowns of COVID-19 cases.
In some dashboard has been added data tables for representing cases
distribution by province/region. Only very few dashboards have been
visualized in COVID-19 test details. Only 6 dashboards have been
compared to global situations. In addition, fatality rate, incidence
rate, ICU beds, stage of the patients \& hospitalize details have been
contained in the several dashboards. These are the most common data
types that have been contained in the dashboards. The main tools that
have been used for different purpose can be shown in the following
table.\hfill\break

>>>>

Dashboards are one of the best visual interpretation methods for
tracking the spread and communication of the COVID-19 pandemic. The 15
dashboards we used in the literature survey are listed in Table 1. We
compared dashboards to identify data types, plotting techniques, colour
themes, and other features such as interactivity on plots and panel
numbers.

@@

Table 03 summarizes the visualization methods used in the dashboards. In
almost every dashboard, value boxes have been used to represent these
total figures. Bar charts and line charts (trend lines) are most
frequently used to visualize this data (confirmed cases, recovered
cases, deaths, and vaccination details) with respect to time. A majority
of dashboards presented data either daily or weekly. The mapping is used
to track the spatial distribution of COVID-19 cases by country,
province, regional etc. When visualizing the data by the map color code
system, circles with respect to the size of the cases have been used to
visualize the variation in size. The considerable number of dashboards
has been used in doughnut-shaped pie charts to represent total COVID-19
confirmed cases, recovered cases, active cases, and deaths as a
percentage. Also, region, gender, age group, and ethnicity can be
identified as common breakdowns of COVID-19 cases. Data tables for
representing case~distribution by province/region have been added to
some dashboards. Very few dashboards have been visualized in the
COVID-19 test details. Only 6 dashboards have been compared to global
situations. In addition, the fatality rate, incidence rate, ICU beds,
stage of the patients, and hospitalized details have been contained in
the several dashboards.\hfill\break
